MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-07-09 MAESTROeX_I/algorithm.tex
add comment for velocity splitting

\subsection{Temporal Integration Scheme}\label{Sec:Temporal Integration Scheme}
We now describe the new temporal integration scheme, which we note can be used for the original base state mapping (with constant base state grid spacing) as well as the new irregularly spaced base state mapping.
Previously we adopted an approach where we split the velocity into a base state component, $w_0(r,t)$, 
and a local velocity $\Ubt(\xb,t)$, so that
\begin{equation}
\Ub = \Ubt(\xb,t) + w_0(r,t)\eb_r,
\end{equation}
where $\eb_r$ is the normal vector in the outward radial direction.
We used $w_0$ to provide an estimate of the base state density evolution over a time step.
This resulted in some unnecessary complications to the temporal integration scheme.
Our new temporal integration scheme does not use this splitting, and is much simpler than the scheme from Paper V since we evolve the velocity directly rather than a more complex evolution equation for the perturbational velocity.
Additionally, the new scheme uses a simpler predictor-corrector approach to the base state density and pressure that no 
longer requires evolution equations and the associated numerical discretizations to update the base state, greatly 
simplifying the algorithm while retaining the same overall second-order accuracy in time.

>>>>

\subsection{Temporal Integration Scheme}\label{Sec:Temporal Integration Scheme}
We now describe the new temporal integration scheme, which we note can be used for the original base state mapping (with constant base state grid spacing) as well as the new irregularly spaced base state mapping.
Previously we adopted an approach where we split the velocity into a base state component, $w_0(r,t)$, 
and a local velocity $\Ubt(\xb,t)$, so that
\begin{equation}
\Ub = \Ubt(\xb,t) + w_0(r,t)\eb_r,
\end{equation}
where $\eb_r$ is the normal vector in the outward radial direction.
We used $w_0$ to provide an estimate of the base state density evolution over a time step.
This resulted in some unnecessary complications to the temporal integration scheme.
Our new temporal integration scheme does not use this splitting, and is much simpler than the scheme from Paper V since we evolve the velocity directly rather than a more complex evolution equation for the perturbational velocity.
\MarginPar{Should emphasize that velocity splitting is still done for projection steps, but full velocity is used to update advection and reactions. Also mention role of $\eta_{\rho}$ here(?)}
Additionally, the new scheme uses a simpler predictor-corrector approach to the base state density and pressure that no 
longer requires evolution equations and the associated numerical discretizations to update the base state, greatly 
simplifying the algorithm while retaining the same overall second-order accuracy in time.
